%\documentclass[margin,11pt]{res}
\documentclass[line,margin]{res} 
%\documentclass{moderncv}
%\documentclass[a4paper,11pt]{article}
\special{papersize=210mm,297mm}

%\usepackage{times}

%for multiline comments
\usepackage{verbatim}

%http://www.math.nyu.edu/student_resources/res.cls
%http://www.mcnabbs.org/andrew/linux/latexres/

%http://blog.oak-tree.us/index.php/2009/11/25/latex-cv-part1

\usepackage[hyphens]{url}
\usepackage[colorlinks=false]{hyperref}
%so when they are printed they are black instead of the grayscale equilivant of blue or whatever

%\usepackage{setspace}
%\doublespace
%\onehalfspace
%\singlespace

%widow and orphan reduction
%\widowpenalty=300
%\clubpenalty=300

%custom shortcuts
\newcommand{\CV}{Curriculum Vit\ae}

%http://www.devdaily.com/blog/post/latex/what-kinds-of-dashes-hyphens-are-available-with-latex
\newcommand{\ampersand}{\&}
\newcommand{\dashsep}{--}
\newcommand{\rangesep}{\dashsep}

\newcommand{\hash}{\#}

\newcommand{\CSharp}{C\hash}

%set-up employer/education position formatting
\begin{format}
\employer{l} \dates{r} \\
\title{l} \location{r} \\
\body\\
\end{format}

\newcommand{\email}{ARobsonSE@hotmail.co.uk}
\newcommand{\emailmailto}{mailto:\email}
\newcommand{\emaillink}{\href{\emailmailto}\email}

\newcommand{\titledoc}{\CV}
\newcommand{\mobilephone}{+44 7411 863293}
\newcommand{\phone}{\mobilephone}

\name{Aaron Robson --- \titledoc}
% \address used twice to have two lines of address
\address{Flat 5, St. Esprit House, 42 High Street, Haverhill, Suffolk. CB9 8AR}
\address{\phone\ --- \emaillink}

\begin{document}
\begin{resume}

\section{Personal Statement}
I am a software developer who endeavours to produce robust and maintainable code.
I pride myself on self-teaching; I have taught myself several programming languages and paradigms in my own time.

While I have gained much real-world experience with my current employer; I look forward to a new challenge with more powerful development tools and processes.

\section{Employment}

\employer{Digi Europe Ltd.}
\title{Junior Software Engineer}
\dates{Sept 2010{\rangesep}Present}
\location{Haverhill, Suffolk}
\begin{position}
Produce Delphi Pascal software (7{\rangesep}XE) within a team for PC based weigh labeller machines.
\begin{itemize} \itemsep -2pt %reduce space between items
	\item Develop new features according to specification on a per customer or general level.
	\item Prepare and document bug-fixes from user reports and by investigating potential causes of errors.
	\item Customer installation and troubleshooting.
	\item Use of version control (Jedi VCS).
	\item Extensions to XML network communication.
	\item Gained experience dealing with heavily threaded real-time applications.
	\item Internal server administration and Technical Support.
	\item Developed a few internal support programs in Python. \comment{Internal backups, network communication with machines, COM port data receiver and log file analysis.}
	\item Made an Android app to send product selection commands.
\end{itemize}
\end{position}

\section{Education}

\employer{University of Lincoln}
\title{Software Engineering B.Sc. --- 2:2 grade}
\dates{2007{\rangesep}2010}
\location{Lincolnshire}
\begin{position}
Technical skills developed through projects, this includes the design and implementation of a blog using ASP.NET and related skills and the backend MySQL database a separate group project where the goal was to create the accommodation booking section of a holiday company website.

During the Software Engineering unit I developed my group skills and theoretical knowledge.
In the Mobile and Distributed Computing unit I was encouraged by the challenge of developing a client server chat program from scratch.
It built upon TCP to make a standardised protocol for handling messaging with an implementation in {\CSharp}.
It had changeable user and room names.
During the final year project developed a natural language analysis program in Python.
\end{position}

\employer{Hills Road Sixth Form College}
\title{College}
\dates{2005{\rangesep}2007}
\location{Cambridge}
\begin{position}
A-Levels in Computing, Maths and Chemistry (grades B, C and D respectfully). \\
AS-Levels in Physics and Critical Thinking.

\begin{comment}
\begin{tabular}{ l r r }
	Computing & A Level & B \\
	Maths & A Level & C \\
	Chemistry & A Level & D \\
	Physics & AS Level & D \\
	Critical Thinking & AS Level & E \\
\end{tabular}
\end{comment}
\end{position}

\employer{Witchford Village College}
\title{Secondary School}
\dates{2002{\rangesep}2005}
\location{Ely, Cambs}
\begin{position}
Nine GCSEs grade C and above, including an A* in Maths and an A in both Science and English.

\begin{comment}
\begin{tabular}{ l r r }
	Mathematics & (a year early) GCSE & A* \\
	Science & Double Award GCSE & AA \\
	English & GCSE & A \\
	History & GCSE & B \\
	Systems {\ampersand} Control & GCSE & B \\
	ICT & Short Course GCSE & C \\
	Statistics & GCSE & C \\
	English Literature & GCSE & C \\
	Geography & GCSE & D \\
	Drama & GCSE & F \\
\end{tabular}
\end{comment}
\end{position}

\section{Experience}
Have experience in the following programming languages and environments: {\CSharp}, Python (and TkInter), Delphi 7, 2007 and XE, Prolog, JavaScript/Ajax, ASP.NET, HTML, CSS, SQL and database design in MSAccess and MySQL. Inspired by Python's itertools module; learning Lisp (primarily the Scheme dialect).
Completed several personal projects including an implementation of John Conway's Game of Life and a numeric base converter, built in Delphi Pascal, {\CSharp} and then Python (v2 and subsequently v3).
I use version control (SVN and Jedi VCS).
Experience in computer construction, maintenance and troubleshooting. Beginner typesetting with {\LaTeX} (including this CV).

\section{Technical \\ Reading}
I have read: \\
Brain of the Firm,
Python in a Nutshell (2nd Edt.),
The Mythical Man-Month (2nd Edt.),
The Pragmatic Programmer,
Code Complete (2nd Edt.),
Surely You're Joking Mr Feynman,
Peopleware (2nd Edt.),
Death March,
Facts and Fallacies of Software Engineering,
Slack,
The Little Schemer (4th Edt.),
13 Things That Don't Make Sense,
The Design of Everyday Things,
Paul Graham essays,
EWD (Dijkstra essays),
other assorted essays and dissertations and
the occasional issue of New Scientist.

I am currently reading: \\
Practical Common Lisp and
Programming Pearls.

\section{Interests}
\begin{itemize} \itemsep -2pt %reduce space between items
	\item Mountain hiking. %Ben Nevis, Scarfell Pike, Snowden, Lake District and the Swiss Alps.
	\item Novels Catch-22, Discworld, Sci-fi.
	\item Supporter of open source software projects; Associate Member of the Free Software Foundation and donator to Python (as AaronR) and VLC.
	\item Enjoy Coding Horror, XKCD and TED.com videos.
	\item A wide taste in music.
	\item Former member of the Scouts and Army Cadets.
\end{itemize}

%Revelation Space (Alasdair Reynolds)
%Ubik - Philip K. Dick
%The Rub\'{a}iy\'{a}t of Omar Khayy\'{a}m (Edward FitzGerald)
%Ringworld (Larry Niven)
%Peace and War (Joe Haldeman)
%A Clockwork Orange (Anthony Burgess)
%Nineteen Eighty-Four (George Orwell)
%First Strike, Fall of Reach (Halo --- dunno how far I got with them)
%The Neutronium Alchemist (Peter F. Hamilton)
%Rainbows End (Vernor Vinge)

\section{References}
Available upon request.

\end{resume}
\end{document}
